quollr: An R Package for Visualizing 2-D Models from Nonlinear Dimension Reductions in High-Dimensional Space

### 2025-12-14 paper-quollr.Rmd
Added another future work

tsne_limb_obj <- fit_highd_model(
  highd_data = data_limb, 
  nldr_data = tsne_limb, 
  b1 = 19, 
  q = 0.1, 
  hd_thresh = 0)

@@

tsne_best_limb_obj <- fit_highd_model(
  highd_data = data_limb, 
  nldr_data = tsne_limb2, 
  b1 = 19, 
  q = 0.1, 
  hd_thresh = 0)

@@

There are several avenues for future development. While hexagonal binning provides a regular structure conducive to modeling, alternative spatial discretizations (e.g., adaptive binning or density-aware tessellations) could be explored to better capture varying data densities. Expanding support for additional distance metrics in the lifting and prediction steps may improve performance across different domains. Additionally, statistical inference tools could be introduced to assess the stability and robustness of the fitted model, which would enhance interpretability and confidence in the outcomes.

>>>>

tsne_limb_obj <- fit_highd_model(
  highd_data = data_limb, 
  nldr_data = tsne_limb, 
  b1 = 21, 
  q = 0.1, 
  hd_thresh = 0)

@@

tsne_best_limb_obj <- fit_highd_model(
  highd_data = data_limb, 
  nldr_data = tsne_limb2, 
  b1 = 21, 
  q = 0.1, 
  hd_thresh = 0)

@@

There are several avenues for future development. While hexagonal binning provides a regular structure conducive to modeling, alternative spatial discretizations (e.g., adaptive binning or density-aware tessellations) could be explored to better capture varying data densities. Expanding support for additional distance metrics in the lifting and prediction steps may improve performance across different domains. Additionally, statistical inference tools could be introduced to assess the stability and robustness of the fitted model, which would enhance interpretability and confidence in the outcomes. Currently, linked plot functionality is limited: selecting a cluster in the `langevitour` controls does not yet highlight the corresponding cluster in the $2\text{-}D$ layout. Implementing this feature in the future would allow users to clearly explore cluster-specific relationships between the `langevitour` and $2\text{-}D$ layout.

### 2025-12-14 paper-quollr.tex
Added another future work

There are several avenues for future development. While hexagonal binning provides a regular structure conducive to modeling, alternative spatial discretizations (e.g., adaptive binning or density-aware tessellations) could be explored to better capture varying data densities. Expanding support for additional distance metrics in the lifting and prediction steps may improve performance across different domains. Additionally, statistical inference tools could be introduced to assess the stability and robustness of the fitted model, which would enhance interpretability and confidence in the outcomes.

>>>>

There are several avenues for future development. While hexagonal binning provides a regular structure conducive to modeling, alternative spatial discretizations (e.g., adaptive binning or density-aware tessellations) could be explored to better capture varying data densities. Expanding support for additional distance metrics in the lifting and prediction steps may improve performance across different domains. Additionally, statistical inference tools could be introduced to assess the stability and robustness of the fitted model, which would enhance interpretability and confidence in the outcomes. Currently, linked plot functionality is limited: selecting a cluster in the \texttt{langevitour} controls does not yet highlight the corresponding cluster in the \(2\text{-}D\) layout. Implementing this feature in the future would allow users to clearly explore cluster-specific relationships between the \texttt{langevitour} and \(2\text{-}D\) layout.
